---
title: "post_prep"
author: "Jake Eisaguirre"
date: "8/15/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}

# librarian downloads, if not already downloaded, and reads in needed packages

librarian::shelf(tidyverse, here, janitor, lubridate, parsedate, stringr)
```

### Load munged data: still need to include swab, amp, etc IDs
```{r}

capture_data <- read_csv(here("data", "merged_AmphibianCaptureSurvey.csv")) %>% 
  clean_names()

ves_data <- read_csv(here("data", "merged_VisualEncounterSurvey.csv")) %>% 
  clean_names()

```
### add day/night binary column
```{r}

cap_data <- capture_data %>% 
  mutate(start_hour = hour(start_time),
         end_hour = hour(end_time),
         survey_time = case_when(start_hour >= 6 & end_hour >= 6 & end_hour < 19 ~ "day", 
                          start_hour >= 19 &  (end_hour < 6 | end_hour <= 23) |
                         (start_hour < 6 & end_hour < 6)~ "night",
                         start_hour >=19 ~"night")) %>% 
  select(!c(start_hour, end_hour))

```

### parse date for ISO 8601
```{r}
cap_date <- cap_data %>% 
  mutate(date = parse_iso_8601(date))
```

### lower case select columns and better naming convention
```{r}

cap <- cap_date %>% 
  mutate(life_stage = str_to_lower(life_stage),
         sex = str_to_lower(sex),
         microhabitat_type = str_to_lower(microhabitat_type)) %>% 
  rename(microhabitat_temperature_c = microhabitat_temperature) %>% 
  rename(body_temperature_c = body_temperature)

```

### pull out cap region table (sites)
```{r}

cap_region_table <- cap %>% 
  select(observer, date, location) 

#%>% 
  # group_by(location) %>% 
  # mutate(temp_reg_id = cur_group_id()) %>% 
  # filter(!duplicated(temp_reg_id)) %>% 
  # select(!c(date, observer))

```

### pull out cap visit table
```{r}

cap_visit_table <- cap %>% 
  select(c(date, survey_time, location)) 

#%>% 
  # group_by(date, survey_time) %>% 
  # mutate(temp_v_id = cur_group_id()) %>% 
  # filter(!duplicated(temp_v_id))

```

### pull out cap survey table - need to figure out duration column
```{r}

cap_survey_table <- cap %>% 
  select(1:5, survey_time) 

# %>%
#   group_by(date, location, start_time, end_time, survey_time) %>%
#   mutate(temp_surv_id = cur_group_id()) %>%
#   filter(!duplicated(temp_surv_id))
#   
  
  
  
  # mutate(start_time = parse_iso_8601(paste(date, start_time, sep= " ")),
  #        end_time = parse_iso_8601(paste(date, end_time, sep = " ")),
  #        duration = hms(end_time - start_time))
  

```

### pull out capture table
```{r}

capture_table <- cap %>% 
  mutate(temp_cap_id = 1:n()) %>% 
  rename(site = location) %>% 
  mutate(site = str_to_lower(site))

write_csv(capture_table, here("clean_tables", "capture.csv"))

```

### clean ves table
```{r}

ves <- ves_data %>% 
  mutate(start_hour = hour(start_time),
         end_hour = hour(end_time),
         survey_time = case_when(start_hour >= 6 & end_hour >= 6 & end_hour < 19 ~ "day", 
                          start_hour >= 19 &  (end_hour < 6 | end_hour <= 23) |
                         (start_hour < 6 & end_hour < 6)~ "night",
                         start_hour >=19 ~"night")) %>% 
  select(!c(start_hour, end_hour)) %>% 
    mutate(date = parse_iso_8601(date))



```

### rbind cap site with ves site and filter by unique occurances
```{r}

site_table <- ves %>% 
  select(observer, date, location) %>% 
  rbind(cap_region_table) %>% 
  group_by(location) %>%  
  mutate(temp_reg_id = cur_group_id()) %>% 
  filter(!duplicated(temp_reg_id)) %>% 
  select(!c(date, observer)) %>% 
  rename(site = location) %>% 
  mutate(site = str_to_lower(site))

write_csv(site_table, here("clean_tables", "site.csv"))

```

### rbind cap visit table with ves and filter by unique occurances
```{r}
visit_table <- ves %>% 
  select(c(date, survey_time, location)) %>% 
  rbind(cap_visit_table) %>% 
  group_by(date, survey_time, location) %>% 
  mutate(temp_v_id = cur_group_id()) %>% 
  filter(!duplicated(temp_v_id)) %>% 
  rename(site = location) %>% 
  mutate(site = str_to_lower(site))

write_csv(visit_table, here("clean_tables", "visit.csv"))


```

### rbind cap survey table with ves and filter by unique occurances - still need to figure out duration column 
```{r}

survey_table <- ves %>% 
  select(1:5, survey_time) %>% 
  rbind(cap_survey_table) %>% 
  group_by(date, location, start_time, end_time, survey_time) %>% 
  mutate(temp_surv_id = cur_group_id()) %>% 
  filter(!duplicated(temp_surv_id)) %>% 
  rename(site = location) %>% 
  mutate(site = str_to_lower(site))

write_csv(survey_table, here("clean_tables", "survey.csv"))  

```

### pull ves table
```{r}

ves_table <- ves %>% 
  mutate(temp_ves_id = 1:n()) %>% 
  rename(site = location) %>% 
  mutate(site = str_to_lower(site))

write_csv(ves_table, here("clean_tables", "visual.csv"))

```

